Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE)

### 2014-02-13 WSSSPE1_report/WSSSPE1_summary_report.tex
Section 3.2:  Keynote 2 strengthened and lengthened.

``Open source is \ldots reproducible by necessity,''
Smith quoted  Fernando Perez~\cite{perez-open-src-reproducible}, explaining that 
reproducibility is a prerequisite for remote collaboration.  He pointed out that GitHub could be the propeller
of the next stage in web development, i.e., ``the Collaborative Web,'' following on from the social web of
Facebook.

>>>>

``Open source is \ldots reproducible by necessity,'' Smith quoted
Fernando Perez~\cite{perez-open-src-reproducible}, explaining that
reproducibility is a prerequisite for remote collaboration.  He
pointed out that GitHub could propel the next stage of web
development, i.e., ``the collaborative web,'' following on from the
social web of Facebook.
